Demo arXiv template

### 2022-10-19 paper/paper.qmd
a draft on the next three paragrpahs in introduction

*indices constructed separately, but there are lots of are same [!], but hard to see from the current construction. "messy data are messy in there own way". Describe how they are same, so we can modular them*

There has not yet been a standardised workflow on index construction. 
For simple indices, users may be able to work out the calculation from the equations or workflow provided, while for more complicated construction, software is not even available for open-source consumption.
Even when the software implementation is available, most indices are computed through a single index command, [given examples but not too domain specific]. 
This software design focuses on the name of the index and includes all the steps in a single index function. 
With this design, there is little room for modification. For example, fit a new distribution that is not provided in the initial code. 
Also, when scaled to a large number of indices, it increases the cognitive load of remembering hundreds of index names. 
A better approach is to modularise these steps and construct a pipeline for users to build indices through choosing different building blocks from each module.
With this design, users focus on the operations involved in the index construction.
If an operation from another index is useful, users can borrow it to modify an existing index.

@@

*this work could be interested to scientists actively developing new indices*

  - domain scientists who propose new indices and directly use indices in analysis. [use multiple indices to compare]
  - general scientists who uses indices as part of analysis, modelling process. The pipeline proposed in the paper opens up the possibility for general scientists to construct indices customised to their research purpose. 
  - statisticians, so as to [draw focus/ advocate] on statistical workflow and software design.

- transparency: official published, can decompose the indices, 
- allow for calculation on uncertainty with randomization, 
- compare indices,
- tweak/ swap building blocks, 
- create new indices based on combinations of existing steps.

The rest of the paper is structured as follows: the concept of data pipeline in R is reviewed in @sec-data-pipeline-in-r.  @sec-a-pipeline-for-building-statistical-indices presents the data pipeline for index construction. @sec-incorporating-new-buliding-blocks-into-the-pipeline explains how to include a new building block in each pipeline module. 
Examples are given in @sec-examples to demonstrate the index construction with the pipeline built.

>>>>

Currently, index construction lacks standardised workflow. 
It is often up to researchers or research institutions to decide whether to provide open source code on the new indices, what would be the best user interface for other researchers to use the new indices, and how easily the new indices can be compared with other existing indices. 
This makes the computation lack transparency and indices cumbersome to experiment with.
Researchers who wish to validate the indices calculated from large institutes need to reinvent the wheels themselves since the source code used for computing is often not available for public consumption.
Open source codes provided by research groups has a narrow margin for exploring other options outside the provided.
Similar steps used by different indices are difficult to spot since the design of user interface for indices often include all the steps under a single function call.
And lastly, it is generally hard to inspect intermediate results during the index construction if users wish to check the output of a certain step.

<!-- Institutes like National Oceanic and Atmospheric Administration (NOAA) and United States Drought Monitor (USDM) moderate indices in their domains. -->
<!-- They provide public information to describe the methodology used in the calculation, publish the index values for public consumption while the source code used for computing is often not available for public consumption.  -->

<!-- For example, many indices involve a step to fit variables into a particular distribution. -->
<!-- Index researchers may provide options for different fits, but it is generally hard to experiment with options outside the provided distributions. -->

<!-- For example, many indices needs standardisation in its workflow, it can be used to rescale the input variables or the index series. -->
<!-- But the current construction does not make it clear through its user interface but sweep it, along with all the other steps in the index construction, under a single function call.  -->

*This week: need to extend each point of why it is beneficial further with more information?*

While every jumbled indices jumble in their own ways, perspicuous indices are all alike. 
This paper proposes a data pipeline for index construction. 
By recognising the common steps shared by many indices, we develop a pipeline that breaks down index construction into multiple modules and allow operations in various modules to be combined like building blocks to construct indices.
The pipeline approach is general in nature while adaptable to most index construction. 
It allows indices to be created, studied and compared in a structured tidy form and enables analysis on indices to be performed easily: 
More specifically, it enables researchers to 1) validate the indices calculated from external organisations, 2) unify various indices under the same framework for comparison, 3) swap or adjust individual steps in the index construction to study their contribution, 4) calculate uncertainty  on indices through bootstrap or others, and finally, 5) inspire proposal of new indices from combining different steps in existing indices.

@@

This work could be interested to researchers actively developing new indices to delivery new indices in an easy-to-reproduce design. 
It would also provide analysts who wish to compute a range of indices in their analysis a uniform interface to build relevant indices from raw data. 
For statistician and software developing engineers, this work frames the workflow of index construction and could motivates similar work in other workflow used in practice.

The rest of the paper is structured as follows: @sec-data-pipeline-in-r reviews the concept of data pipeline in R. 
The pipeline framework for index construction is presented in @sec-a-pipeline-for-building-statistical-indices.  @sec-incorporating-new-buliding-blocks-into-the-pipeline explains how to include a new building block in each pipeline module. 
Examples are given in @sec-examples to demonstrate the index construction with the pipeline built.

### 2022-10-19 paper/paper.tex
a draft on the next three paragrpahs in introduction

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\emph{indices constructed separately, but there are lots of are same
{[}!{]}, but hard to see from the current construction. ``messy data are
messy in there own way''. Describe how they are same, so we can modular
them}

There has not yet been a standardised workflow on index construction.
For simple indices, users may be able to work out the calculation from
the equations or workflow provided, while for more complicated
construction, software is not even available for open-source
consumption. Even when the software implementation is available, most
indices are computed through a single index command, {[}given examples
but not too domain specific{]}. This software design focuses on the name
of the index and includes all the steps in a single index function. With
this design, there is little room for modification. For example, fit a
new distribution that is not provided in the initial code. Also, when
scaled to a large number of indices, it increases the cognitive load of
remembering hundreds of index names. A better approach is to modularise
these steps and construct a pipeline for users to build indices through
choosing different building blocks from each module. With this design,
users focus on the operations involved in the index construction. If an
operation from another index is useful, users can borrow it to modify an
existing index.

@@

\emph{this work could be interested to scientists actively developing
new indices}

\begin{itemize}
\tightlist
\item
  domain scientists who propose new indices and directly use indices in
  analysis. {[}use multiple indices to compare{]}
\item
  general scientists who uses indices as part of analysis, modelling
  process. The pipeline proposed in the paper opens up the possibility
  for general scientists to construct indices customised to their
  research purpose.
\item
  statisticians, so as to {[}draw focus/ advocate{]} on statistical
  workflow and software design.
\end{itemize}

\begin{itemize}
\tightlist
\item
  transparency: official published, can decompose the indices,
\item
  allow for calculation on uncertainty with randomization,
\item
  compare indices,
\item
  tweak/ swap building blocks,
\item
  create new indices based on combinations of existing steps.
\end{itemize}

The rest of the paper is structured as follows: the concept of data
pipeline in R is reviewed in Section~\ref{sec-data-pipeline-in-r}.
Section~\ref{sec-a-pipeline-for-building-statistical-indices} presents
the data pipeline for index construction.
Section~\ref{sec-incorporating-new-buliding-blocks-into-the-pipeline}
explains how to include a new building block in each pipeline module.
Examples are given in Section~\ref{sec-examples} to demonstrate the
index construction with the pipeline built.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, frame hidden, interior hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

Currently, index construction lacks standardised workflow. It is often
up to researchers or research institutions to decide whether to provide
open source code on the new indices, what would be the best user
interface for other researchers to use the new indices, and how easily
the new indices can be compared with other existing indices. This makes
the computation lack transparency and indices cumbersome to experiment
with. Researchers who wish to validate the indices calculated from large
institutes need to reinvent the wheels themselves since the source code
used for computing is often not available for public consumption. Open
source codes provided by research groups has a narrow margin for
exploring other options outside the provided. Similar steps used by
different indices are difficult to spot since the design of user
interface for indices often include all the steps under a single
function call. And lastly, it is generally hard to inspect intermediate
results during the index construction if users wish to check the output
of a certain step.

\emph{This week: need to extend each point of why it is beneficial
further with more information?}

While every jumbled indices jumble in their own ways, perspicuous
indices are all alike. This paper proposes a data pipeline for index
construction. By recognising the common steps shared by many indices, we
develop a pipeline that breaks down index construction into multiple
modules and allow operations in various modules to be combined like
building blocks to construct indices. The pipeline approach is general
in nature while adaptable to most index construction. It allows indices
to be created, studied and compared in a structured tidy form and
enables analysis on indices to be performed easily: More specifically,
it enables researchers to 1) validate the indices calculated from
external organisations, 2) unify various indices under the same
framework for comparison, 3) swap or adjust individual steps in the
index construction to study their contribution, 4) calculate uncertainty
on indices through bootstrap or others, and finally, 5) inspire proposal
of new indices from combining different steps in existing indices.

@@

This work could be interested to researchers actively developing new
indices to delivery new indices in an easy-to-reproduce design. It would
also provide analysts who wish to compute a range of indices in their
analysis a uniform interface to build relevant indices from raw data.
For statistician and software developing engineers, this work frames the
workflow of index construction and could motivates similar work in other
workflow used in practice.

The rest of the paper is structured as follows:
Section~\ref{sec-data-pipeline-in-r} reviews the concept of data
pipeline in R. The pipeline framework for index construction is
presented in
Section~\ref{sec-a-pipeline-for-building-statistical-indices}.
Section~\ref{sec-incorporating-new-buliding-blocks-into-the-pipeline}
explains how to include a new building block in each pipeline module.
Examples are given in Section~\ref{sec-examples} to demonstrate the
index construction with the pipeline built.
